---
title: 2018 enrollment - other options - DRAFT
author: Betsy Rosalen
date: '2019-12-27'
slug: /2018-enrollment-other-options/
categories: []
tags: 
    - enrollment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
library(kableExtra)
library(DT)
library(magrittr)
library(stringr)
library(htmlTable)
```

```{r data}
# Import numerical data columns
data <- read.csv("S:/DicovererWorkbooks/Workbook2.csv", header=FALSE, stringsAsFactors = FALSE, skip = 5)

# Import headers
head1 <- c("", "", rep("Undergraduate",3), rep("Graduate",3), "")
head2 <- c("SenCom", "College", rep(c("Full-time", "Part-time", "Total"),2), "Total")

cols <- paste(head1, head2, sep = " ", collapse = NULL)
cols <- trimws(cols)

# Set headers 
names(data) <- cols

# Make total rows uppercase
data$SenCom <- toupper(data$SenCom)

# Combine first two columns
data$College <- ifelse(data$College == "", data$SenCom, data$College)
data <- data[-1]

# Calculate totals
data['Total Full-time'] <- rowSums(data[,c(2,5)], na.rm=TRUE)
data['Total Part-time'] <- rowSums(data[,c(3,6)], na.rm=TRUE)

# Reorder columns
data <- data[c(1:7,9,10,8)]

# Reorder rows
data <- data[c(2:19,1,21:27,20,28),]
row.names(data) <- NULL

# Rename Last row
data[28,1] <- "TOTAL UNIVERSITY"

# ---------------------------------------------------------------------------- #
# Format numbers - DOES NOT WORK!!!
#data[2:10] <- format(data[2:10], big.mark   = ",")
#data[is.na.data.frame(data)] <- ""
# NONE OF THE ABOVE FORMATTING WORKS!  When done this way, can't stop NA from printing.
# ---------------------------------------------------------------------------- #

table_title <- "Total Enrollment by Undergraduate and Graduate Level, Full-time/Part-time Attendance, and College - Fall 2018"
```

## kableExtra with advanced styling

##### `r table_title`

```{r kableExtra_advanced_2, results='asis'}

data2 <- data
names(data2) <- c("College", rep(c("Full-time", "Part-time", "Total"), 3))

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3),
                   extra_css = "border-bottom: 1px solid",
                   background = "#ebf1fd", 
                   bold = TRUE) %>%
  row_spec(c(0), bold = TRUE, background = "#ebf1fd", 
           extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(19,27, 28), bold = TRUE, background = "#ebf1fd") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## kableExtra with advanced styling part 2

##### `r table_title`

```{r kableExtra_advanced, results='asis'}

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3), 
                   color = "white", 
                   background = "#465e8c", 
                   bold = TRUE) %>%
  row_spec(c(0,28), color = "white", background = "#465e8c") %>%
  row_spec(c(19,27), color = "white", background = "#787878") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## DT

```{r DT, results='asis'}
data %>%
  datatable(caption = table_title, 
            class = 'stripe hover compact table-condensed', 
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            #style = 'default'
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## DT with double header

**No Bootstrap theme is used here.**

**Double header doesn't download properly with the excel, pdf etc... buttons.**

**Problem is that the reason that these columns are formatted so nicely and evenly-spaced is because the header labels are shorter and so the columns do not have to be expanded to fit the text.  If we want shorter header names we may have to make more tables with less columns.**

**There's also no way that I have found so far to format the total rows to be a different color to separate them out from the colleges, so we may want to remove the total and subtotal rows.**

```{r DT_styled, results='asis'}

# a custom table container
double_header = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, 'College'),
      th(colspan = 3, 'Undergraduate'),
      th(colspan = 3, 'Graduate'),
      th(colspan = 3, 'Total')
    ),
    tr(
      lapply(rep(c("Full-time", "Part-time", "Total"), 3), th)
    )
  )
))

data %>%
  datatable(container = double_header, 
            caption = table_title,  
            class = 'stripe hover compact nowrap table-condensed',
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## htmlTable

```{r}
htmlTable(data, rnames=FALSE, #total=TRUE,
          #col.rgroup = c("none", "#F7F7F7"),
          col.columns = c("none", rep(c("none", "none", "#F5FBFF"), 3)),
          total = "tspanner",
          css.total = rep("border-top: 1px solid grey; font-weight: 900; background: #F7F7F7", 3),
          tspanner = c("Senior Colleges", "Community Colleges", "Grand Total"),
          n.tspanner = c(19, 8, 1))
```

